Alleviating the Topology Mismatch Problem in Unstructured and Structured Overlay Networks: A Survey

### 2014-01-26 structured.tex
2012.09.06 (Vassilis) Algorithm depiction reworked.
2012.10.08 (Vassilis) Text added explaining the three indicators (low, medium, high) for each of the criteria against which the algorithms are evaluated (efficiency, overhead, scalability). Filled in missing references and question marks in the tables and text. Intro and background reworked. First page shows the full abstract and bar charts calibrated (orientation, axis labels etc). Text now conforms to ACM Computing Surveys style/format.

This section focuses on the structured P2P architectures. The following
paragraphs contain a thorough discussion and analysis of the algorithms proposed
in the literature for dealing with the topology mismatch problem in such
architectures. In structured P2P systems, the construction of the routing tables
in every participating node determines the efficiency of message forwarding.
Therefore, routing tables that represent the underlying physical structure well
can achieve increased performance. For this reason, the proposed methods for
topology mismatch problem basically use different levels of proximity
information to optimize them towards this direction. The algorithms are here
categorised based the previous work done by
\cite{castro_proximitydht_2002,castro_topawareroute_2002,ratnasamy_openq_2002}.

@@

\textit{Global Soft-State} \cite{xu_globstate_2003} builds a global map to help
choose shorter routing paths, combining the landmark binning method and small
scale distance probes to reveal the proximity properties of the underlying
network to the overlay. Figure \ref{fig:global_softstate} presents the landmark
space and the mapping of the position of the nodes. This global view of the
state is made available to all nodes in order to help them find the best way to
route their messages. \textit{Global Soft-State} operates in two main stages,
generation and use of the proximity information. For generating the proximity
information a hybrid approach is proposed, which uses landmark clustering as a
preprocessing step in order to select a number of potential nearest neighbour
candidates and then refine the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. For using
the proximity information, the algorithm chooses a different path from the
classic gossiping approaches for constructing and maintaining the overlay. It is
based on landmark clustering for strategic placement of proximity information on
the overlay enabling any node to access such information using a landmark number
that reflects its physical position in the network. For various logical
regions\footnote{This might be a high-order zone in the eCAN\cite{xu_ecan_2002}
context or a set of nodes sharing a particular prefix in overlays such as
Pastry.} maps of physical information are built and published where each node
may appear in a maximum of $log\left( N \right)$ such maps. To dynamically adapt
to changing network conditions, a node subscribes to relevant \emph{soft states}
that utilize a notification system in order to initialize any necessary
neighbour re-selection.

@@

%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{xu_globstate_2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multicast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighbourhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximatelly 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sucrificing the the decentralised nature of DHTs and
% thus poorly scalling.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Mithos}
\emph{Mithos} \cite{waldvogel_mythos_2003} is a P2P protocol which incorporates
directed incremental probing to find near optimal node placement, and is
classified by its authors as an integration of geographic layout and proximity
routing overlay optimization methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{wu_laptop_2007}, organises the overlay into a tree-based
hierarchy with main focus on reducing hops during message routing as well as
minimizing maintenance overhead. Additionally, a caching scheme is also
incorporated so as to further reduce routing table update costs. The authors
theoretically show that in LAPTOP routing path length is bounded by $O(log_d N)$
and node joining and leaving in the overlay network is bounded by
$O\left( d log_d N \right)$ hops in a balanced overlay tree, where $N$ is the
number of nodes, and $d$ is the maximum degree of each node. LAPTOP implements
the geographical layout approach  and constructs its layout in a self-organizing
and efficient fashion, by estimating the round-trip times to a small number of
nodes in the overlay network in order to make them roughly aware of their
physical distances among them.

@@

\emph{Proximity in Kademlia} \cite{kaune_pkad_2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distingushes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimisation. One falling into
{\em proximity routing} and the other on {\em proximity neighbour selection}
approaches overlay optimization techiques for exploiting proximity. For the
first, the goal is in choosing the best next hop during routing a message. Due
to the fact that the routing in Kademlia is iterative, it is the initiator of
the lookup that chooses each next hop from a set of candidate nodes. Standard
Kedemlia always chooses the closest node with respect to the XOR metric but with
proximity routing selection, Kademlia chooses the one with the smallest underlay
metric cost. Thus, as in all such approaches, there is a trade-off between the
overlay and underlay distances.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{morimoto_chop6_2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord, CHOP6 uses a finger table, whose entries hold more than
one candidate node.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{shi_t2mc_2008} uses traceroute logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the traceroute to initialize the
centroinds of two sets. Then the peer calculates, for all hops allong its
tracerouted path, the absolute distance to these centroids of both sets and
assigns the routers to that centroid with which it has the smaller absolute
distance. After that, the mean and variance values are calculated and if the
variance is larger than a predefined threshold then the algorithm sets the two
latency mean values as new centroids for the two sets and loops again.
Ultimately peer will end up with two sets having the minimum intra-set variance.
The peer, then, chooses the router from the second set with the minimum hops
attribute and sets it as a threshold. The selected router and all others whose
hops attribute is larger than the threshold are classified as \emph{remote}
router cluster. The remaining are classified as \emph{near}. From the near
class, the peer chooses the one with maximum hops attribute as its edge router,
and registers it along with the all the near cluster into the DHT of the P2P
overlay. As new peers join the network, those that share the same edge router
or any of the members of the near router clustersm there would gather to form a
close peer cluster. As Edge routers can provide more valuable information than
other members of the near set, T2MC was designed to prioritize interaction of
peers and edge gateways.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% traceroute is a very heavy tool and thus incurs excessive burden to the
% network resourses.
high &
% Traceroute is categorised as too heavy-weighted and intrucive for use in a
% larger scale system \cite{ratnasamy_binning_2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PChord}
\emph{PChord}\cite{hong_pchord_2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. The overlay
maintenance cost can be considered similar to Chord's since besides node
join/leave and cost of finger table entries heartbeat, PChord adds heartbeat of
nodes inside the proximity list but since this list always contains nodes with
the lowest RTT the added cost is kept to a minimal.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AChord}
\emph{AChord} \cite{dao_achord_2006} uses IPv6's anycast mechanism in order to
releave the protocol from complex joining procedures, and achieve high accuracy
of network proximity giving high routing efficiency, Anycast delivers a message
comming from the outside of an anycast group to the physicaly closest node in
that group. AChord organizes all nodes participating in the overlay network into
an anycast group. Any joining node comes outside of that group and, thus, is
automaticaly forwarded to the physicaly nearest node in order to bootstrap,
avoiding the need to, explicitly, maintain such nodes, and the effort of finding
a way of locating the physically nearest among them. The ID of the new comming
node is computed based on the ID of the bootstrap node and the bootstrap's
predecessor in a way that the constructed ID will be positioned between the
aformentioned two. After joining, the finger table is build the same way as in
the Chord protocol. Moreover, additional nodes are maintained in a structure
called \emph{neighbourship table} which stores information about the closest
known node. The routing decision is made by using both the neighbourship and
the finger table. The authors claim this to be a lightweight approach that
requires few changes to Chord in order not to affecting its own advantageous
characteristics.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Chord6}
\emph{Chord6} \cite{xiong_chord6_2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces inter-domain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{DHT-PNS}
The work in \cite{hancong_pnsbased_2006} propose a proximity neighbour selection
scheme on top of the Chord DHT. The main goal is to use proximity information
to group physically close by nodes as neighbours in the DHT table. In order to
detect proximity, virtual network coordinates of peers are used, by using the
Vivaldi protocol \cite{cox_vivaldi_2004}. The virtual coordinates are then used
by the nodes to map to identifier space in the DHT. The space is partitioned
using a \emph{concentric circle clustering scheme} where successive cycles of
radiuses $\rho$, $2\rho$, $3\rho$ and so on, are constructed. Then the formed
annuluses are divided into $2\chi-1$ \emph{sectors}, where $\chi$ denotes the
sequence number of the annulus starting from $\chi = 1$ for the centre cycle. It
is proved in the paper, that this way each sector occupies the same area as does
the center cycle. Assuming uniform node distribution, this characteristic,
favours a more load balanced clustering operation. Every sector in this $2d$
coordinate space is mapped to a unique \emph{region} in the DHT space forming a
multi-layer node identifier space.  Thus, any nodes that belong to the same
sector, are mapped to the same region as well, preserving their proximity
relationship unveiled by the use of the Vivaldi protocol. The individual pieces
are mapped to the identifier space uniquely, allowing logarithmic lookup
operations with high probability on Chord. The system described in the previous
section allows any node to obtain its DHT key and its region key, in a fully
distributed manner, just by applying a consistent hash function. Using an RPC
call in Chord, the node can obtain the region's master node, called
\emph{Cluster Node (CN)} which is responsible for clustering the nodes belonging
in the same sector or region with that of the node at hand. An additional RPC
call, registers it to its corresponding region and publishes its information,
through the special peer CN. The node can, additionaly, ask CN for other
nodes that have previously joined the region in order to add them into its
neighbour set for future routing table optimization. Even in the case when no
neighbour is detected in the current region, the search is expanded to adjasent
regions and towards an upper layer identifier space until one is found or the
first layer reached.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{sun_quasi_2008}, tries
to address the topology mismatch problem, at the construction phase of the
Chord identifier cycle, on the the basis of underlying topology information.
The proposed model constructs the \emph{Quasi-Chord} ovelay network in three
steps. First, each host acquires its coordinates in the geometric space
utilizing the \emph{global network position (GNP)} protocol \cite{ng_gnp_2001}.
Second, using the \emph{Cantor space filling curve}, the $2$-dimensional space
is converted to a $1$-dimensional one, used in the last, third, step to build
the Quasi-Chord circle according to the host's Cantor value. In Quasi-Chord
each node stores 2 finger tables; one clockwise and one counter-clockwise.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The algorithm shows to reduce end-to-end delay as well as not produce
% duplicates of messages.
medium &
% The overhead is more compared to vanilla chord since mapping of 2-dimensional
% space to 1-demensional with Cantor SPF adds some extra burden in time
% complexity. Also the addition of the couter-clockwise finger table doubles the
% data, per se, needed to be stored and maintained.
high &
% The GNP system is a static landmark approach making things not fully
% distributed and thus constrain the model's scalability.
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{IP-based Clustering (IPBC)}
Proximity neighbour selection algorithms use probing and other techniques to
detect proximity. However, such methods are either not precise enough, or
overload the network. \emph{IP-based clustering} \cite{karwaczynski_ipbc_2007}
is a proximity neighbour selection based algorithm in which the authors propose
to use the IP address prefixes (16 bit for IPv4) in order to detect proximity.
\cite{freedman_iploc_2005} states that $97\%$ of prefixes larger than $24$ bits
belong to a single geographical location. However, using less number of bits
creates less precise results and more number of bits increase the burden on the
network and reduce the possible number of neighbours. Therefore, a careful
selection is required in terms of performance/accuracy tradeoff. IP-based
Clustering generates a key and its prefix and stores the later in the DHT
itself, so that any newly joining nodes with the same IP prefix can query it and
identify all the neighbours with the same one relatively easy. Nodes
periodically update their entries in the DHT by removing those who leave, or
those who has been timed out with no further activity detected from the node.

@@

>>>>

This section focuses on the structured P2P architectures. The following
paragraphs contain a thorough discussion and analysis of the algorithms proposed
in the literature for dealing with the topology mismatch problem in such
architectures. In structured P2P systems, the construction of the routing tables
in every participating node determines the efficiency of message forwarding.
Therefore, routing tables that represent the underlying physical structure well
can achieve increased performance. For this reason, the proposed methods for
topology mismatch problem basically use different levels of proximity
information to optimize them towards this direction. The algorithms are here
categorised based the previous work done by \cite{CDHR2002,CDCR2002,RSS2002}.

@@

\textit{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths, combining the landmark binning method and small
scale distance probes to reveal the proximity properties of the underlying
network to the overlay. Figure \ref{fig:global_softstate} presents the landmark
space and the mapping of the position of the nodes. This global view of the
state is made available to all nodes in order to help them find the best way to
route their messages. \textit{Global Soft-State} operates in two main stages,
generation and use of the proximity information. For generating the proximity
information a hybrid approach is proposed, which uses landmark clustering as a
preprocessing step in order to select a number of potential nearest neighbour
candidates and then refine the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. For using
the proximity information, the algorithm chooses a different path from the
classic gossiping approaches for constructing and maintaining the overlay. It is
based on landmark clustering for strategic placement of proximity information on
the overlay enabling any node to access such information using a landmark number
that reflects its physical position in the network. For various logical
regions\footnote{This might be a high-order zone in the eCAN\cite{xu_ecan_2002}
context or a set of nodes sharing a particular prefix in overlays such as
Pastry.} maps of physical information are built and published where each node
may appear in a maximum of $log\left( N \right)$ such maps. To dynamically adapt
to changing network conditions, a node subscribes to relevant \emph{soft states}
that utilize a notification system in order to initialize any necessary
neighbour re-selection.

@@

%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multicast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighbourhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximatelly 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralised nature of DHTs and
% thus poorly scalling.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Mithos}
\emph{Mithos} \cite{WR2003} is a P2P protocol which incorporates directed
incremental probing to find near optimal node placement, and is classified by
its authors as an integration of geographic layout and proximity routing overlay
optimization methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organises the overlay into a tree-based hierarchy
with main focus on reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. The authors theoretically show
that in LAPTOP routing path length is bounded by $O(log_d N)$ and node joining
and leaving in the overlay network is bounded by $O\left( d log_d N \right)$
hops in a balanced overlay tree, where $N$ is the number of nodes, and $d$ is
the maximum degree of each node. LAPTOP implements the geographical layout
approach  and constructs its layout in a self-organizing and efficient fashion,
by estimating the round-trip times to a small number of nodes in the overlay
network in order to make them roughly aware of their physical distances among
them.

@@

\emph{Proximity in Kademlia} \cite{KLKP2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distingushes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimisation. One falling into
{\em proximity routing} and the other on {\em proximity neighbour selection}
approaches overlay optimization techiques for exploiting proximity. For the
first, the goal is in choosing the best next hop during routing a message. Due
to the fact that the routing in Kademlia is iterative, it is the initiator of
the lookup that chooses each next hop from a set of candidate nodes. Standard
Kedemlia always chooses the closest node with respect to the XOR metric but with
proximity routing selection, Kademlia chooses the one with the smallest underlay
metric cost. Thus, as in all such approaches, there is a trade-off between the
overlay and underlay distances.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{MT2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord, CHOP6 uses a finger table, whose entries hold more than
one candidate node.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{SLCGZ2008} uses traceroute logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the traceroute to initialize the
centroinds of two sets. Then the peer calculates, for all hops allong its
tracerouted path, the absolute distance to these centroids of both sets and
assigns the routers to that centroid with which it has the smaller absolute
distance. After that, the mean and variance values are calculated and if the
variance is larger than a predefined threshold then the algorithm sets the two
latency mean values as new centroids for the two sets and loops again.
Ultimately peer will end up with two sets having the minimum intra-set variance.
The peer, then, chooses the router from the second set with the minimum hops
attribute and sets it as a threshold. The selected router and all others whose
hops attribute is larger than the threshold are classified as \emph{remote}
router cluster. The remaining are classified as \emph{near}. From the near
class, the peer chooses the one with maximum hops attribute as its edge router,
and registers it along with the all the near cluster into the DHT of the P2P
overlay. As new peers join the network, those that share the same edge router
or any of the members of the near router clustersm there would gather to form a
close peer cluster. As Edge routers can provide more valuable information than
other members of the near set, T2MC was designed to prioritize interaction of
peers and edge gateways.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% traceroute is a very heavy tool and thus incurs excessive burden to the
% network resourses.
high &
% Traceroute is categorised as too heavy-weighted and intrucive for use in a
% larger scale system \cite{RHMKS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PChord}
\emph{PChord}\cite{HLYW2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. The overlay
maintenance cost can be considered similar to Chord's since besides node
join/leave and cost of finger table entries heartbeat, PChord adds heartbeat of
nodes inside the proximity list but since this list always contains nodes with
the lowest RTT the added cost is kept to a minimal.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AChord}
\emph{AChord} \cite{DK2006} uses IPv6's anycast mechanism in order to
releave the protocol from complex joining procedures, and achieve high accuracy
of network proximity giving high routing efficiency, Anycast delivers a message
comming from the outside of an anycast group to the physicaly closest node in
that group. AChord organizes all nodes participating in the overlay network into
an anycast group. Any joining node comes outside of that group and, thus, is
automaticaly forwarded to the physicaly nearest node in order to bootstrap,
avoiding the need to, explicitly, maintain such nodes, and the effort of finding
a way of locating the physically nearest among them. The ID of the new comming
node is computed based on the ID of the bootstrap node and the bootstrap's
predecessor in a way that the constructed ID will be positioned between the
aformentioned two. After joining, the finger table is build the same way as in
the Chord protocol. Moreover, additional nodes are maintained in a structure
called \emph{neighbourship table} which stores information about the closest
known node. The routing decision is made by using both the neighbourship and
the finger table. The authors claim this to be a lightweight approach that
requires few changes to Chord in order not to affecting its own advantageous
characteristics.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Chord6}
\emph{Chord6} \cite{XZHL2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces inter-domain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{DHT-PNS}
The work in \cite{DLTZZ2006} propose a proximity neighbour selection
scheme on top of the Chord DHT. The main goal is to use proximity information
to group physically close by nodes as neighbours in the DHT table. In order to
detect proximity, virtual network coordinates of peers are used, by using the
Vivaldi protocol \cite{cox_vivaldi_2004}. The virtual coordinates are then used
by the nodes to map to identifier space in the DHT. The space is partitioned
using a \emph{concentric circle clustering scheme} where successive cycles of
radiuses $\rho$, $2\rho$, $3\rho$ and so on, are constructed. Then the formed
annuluses are divided into $2\chi-1$ \emph{sectors}, where $\chi$ denotes the
sequence number of the annulus starting from $\chi = 1$ for the centre cycle. It
is proved in the paper, that this way each sector occupies the same area as does
the center cycle. Assuming uniform node distribution, this characteristic,
favours a more load balanced clustering operation. Every sector in this $2d$
coordinate space is mapped to a unique \emph{region} in the DHT space forming a
multi-layer node identifier space.  Thus, any nodes that belong to the same
sector, are mapped to the same region as well, preserving their proximity
relationship unveiled by the use of the Vivaldi protocol. The individual pieces
are mapped to the identifier space uniquely, allowing logarithmic lookup
operations with high probability on Chord. The system described in the previous
section allows any node to obtain its DHT key and its region key, in a fully
distributed manner, just by applying a consistent hash function. Using an RPC
call in Chord, the node can obtain the region's master node, called
\emph{Cluster Node (CN)} which is responsible for clustering the nodes belonging
in the same sector or region with that of the node at hand. An additional RPC
call, registers it to its corresponding region and publishes its information,
through the special peer CN. The node can, additionaly, ask CN for other
nodes that have previously joined the region in order to add them into its
neighbour set for future routing table optimization. Even in the case when no
neighbour is detected in the current region, the search is expanded to adjasent
regions and towards an upper layer identifier space until one is found or the
first layer reached.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{SZ2008}, tries
to address the topology mismatch problem, at the construction phase of the
Chord identifier cycle, on the the basis of underlying topology information.
The proposed model constructs the \emph{Quasi-Chord} ovelay network in three
steps. First, each host acquires its coordinates in the geometric space
utilizing the \emph{global network position (GNP)} protocol \cite{ng_gnp_2001}.
Second, using the \emph{Cantor space filling curve}, the $2$-dimensional space
is converted to a $1$-dimensional one, used in the last, third, step to build
the Quasi-Chord circle according to the host's Cantor value. In Quasi-Chord
each node stores 2 finger tables; one clockwise and one counter-clockwise.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The algorithm shows to reduce end-to-end delay as well as not produce
% duplicates of messages.
medium &
% The overhead is more compared to vanilla chord since mapping of 2-dimensional
% space to 1-demensional with Cantor SPF adds some extra burden in time
% complexity. Also the addition of the counter-clockwise finger table doubles
% the data, per se, needed to be stored and maintained.
high &
% The GNP system is a static landmark approach making things not fully
% distributed and thus constrain the model's scalability.
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{IP-based Clustering (IPBC)}
Proximity neighbour selection algorithms use probing and other techniques to
detect proximity. However, such methods are either not precise enough, or
overload the network. \emph{IP-based clustering} \cite{KM2007} is a proximity
neighbour selection based algorithm in which the authors propose to use the IP
address prefixes (16 bit for IPv4) in order to detect proximity.
\cite{freedman_iploc_2005} states that $97\%$ of prefixes larger than $24$ bits
belong to a single geographical location. However, using less number of bits
creates less precise results and more number of bits increase the burden on the
network and reduce the possible number of neighbours. Therefore, a careful
selection is required in terms of performance/accuracy tradeoff. IP-based
Clustering generates a key and its prefix and stores the later in the DHT
itself, so that any newly joining nodes with the same IP prefix can query it and
identify all the neighbours with the same one relatively easy. Nodes
periodically update their entries in the DHT by removing those who leave, or
those who has been timed out with no further activity detected from the node.

@@

\input{structured-plot}
